\byline{\Large The ``Nammies'' Song}{Tom Hollow}
Who would have thought that Chelsea Hollow would grow into the beautiful and
talented woman she is today. Well her mother and I always knew she would be.
From waking up singing the ``Good Morning'' song to bedtime with the calming
``Nammies'' song, Chesea's day was filled with singing, dancing and playing. Her
first word was “shoe” spoken in a most melodic way with a hint of a Swedish
accent. Chelsea was always comfortable on stage, performing and singing since
pre-school with that ever-present smile and happy attitude.

Some of my fondest memories of Chelsea growing up were simple daddy and me
moments. When Grace was working Saturdays, Chelsea and I could be found watching
those silly blue ``Smurfs'' or taking an underwater adventure with ``The Snorks.''
Then it was off to breakfast at Eggs and Things before returning home to play
in the garden or off to the beach to skim. In the evening we would sit on the
front porch watching the waterfall and try to guess which direction the next
car would come from. 

Through the years Chelsea has been the source of such joy and pride.  Those
feelings continue to this day as she prepares for the next journey in her
wonderful life. It brings to mind the day of her birth. Grandma Anna and I had
just returned from the hospital bubbling with joy at the birth of this perfect
and beautiful baby. I put on a Stevie Wonder album and we both danced happily
while listening to those lyrics that seemed written for Chelsea ``Isn’t she
lovely, made from love.''

\bigskip
